---
title: "Pokemon Analysis"
output: html_notebook
---

# Introduction

## Introduction to Pokemon

Pokemon is a series of video games published by Nintendo where a player can take an adventure through their region. While on your adventure, you will encounter many Pokemon and have the opportunity to both capture and battle them. 

In this project, we will explore the various traits and attributes of pokemon, and dive into predicting which Pokemon will win in a battle against other Pokemon. 

## Libraries Needed
```{r, message = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

## Loading the Dataset: 
```{r}
# We will begin with pokemon.csv first and do some EDA on the file
pokemon <- read_csv('pokemon.csv')
head(pokemon)
```

Since each column has spaces, we want to reformat it so it will be easier to perform data analysis on them. 

```{r}
names(pokemon) <- gsub(" ", "_", names(pokemon))
names(pokemon) <- gsub("\\.", "", names(pokemon))
names(pokemon) <- tolower(names(pokemon))
head(pokemon)
```


# Exploratory Data Analysis

Let's begin by exploring each Pokemon type. 

However, Pokemon may have two types and we want to count these type frequencies including their second type. To do this, we will make a new dataframe before making our boxplot directly, and sum up their types there. 

```{r, include = FALSE}
# For aesthetic reasons
setcolors = c("Fire" = "#EE8130", "Normal" = "#A8A77A", "Water" = "#6390F0", "Grass" = "#7AC74C", "Electric" = "#F7D02C", "Ice" = "#96D9D6", "Fighting" = "#C22E28", "Poison" = "#A33EA1", "Ground" = "#E2BF65", "Flying" = "#A98FF3", "Psychic" = "#F95587", "Bug" = "#A6B91A", "Rock" = "#B6A136", "Ghost" = "#735797", "Dragon" = "#6F35FC", "Dark" = "#705746", "Steel" = "#B7B7CE", "Fairy" = "#D685AD")
fill_colors = scale_fill_manual(values = setcolors)
```

```{r}
types_count <- table(pokemon$type_1) + table(pokemon$type_2)
types_count_df <- as.data.frame(types_count)
```


```{r}
ggplot(data = types_count_df, aes(x = reorder(Var1, Freq), y = Freq, fill = Var1)) + geom_bar(stat = "identity") + fill_colors + coord_flip() + labs(title = "Distribution of Pokemon Types", x = "Type", y = "Frequency")
```

